Natural selection in the Health and Retirement Study

### 2023-09-18 hrs-selection.qmd
Bugfixes

# TODO: ratio to family poverty threshold, h10inpovr
# 
# TODO: is ADHD reverse-coded? What about XDISORDER?

@@

# for a confidence interval
significant <- function (x) {
  stopifnot(is.numeric(x), length(x) == 2)
  x[1] < 0 && x[2] > 0
}

@@

The HRS contains weights which match survey respondents to the US population. I use weights for the biomarker subsample (\*BIOWGTR in the HRS tracker file). Since half the sample enters the extended interview including biomarker data in each biannual survey, I weight individuals by either their 2010 weight or their 2012 weight. This maximizes the available sample of both black and white respondents, and should approximately match the US population of the sample cohorts between 2010 and 2012.

@@

tails_boot_fert <- map(cors_fert_edu, 
                       \(x) x + c(-1.96, 1.96) * SE(x))

tails_boot_sibs <- map(cors_sibs_edu, 
                       \(x) x + c(-1.96, 1.96) * SE(x))

>>>>

# TODO: ratio to family poverty threshold, h10inpovr
# 
# Is ADHD reverse-coded? - Doesn't seem to be, correlates negatively
#       with income
# What about XDISORDER?
# ADHD doesn't seem to be. Nor does XDISORDER (correlates with e.g. r*depres)

@@

# for a confidence interval
significant <- function (x) {
  stopifnot(is.numeric(x), length(x) == 2)
  all(x < 0) || all(x > 0)
}

@@

The HRS contains weights which match survey respondents to the US population. I use weights for the biomarker subsample (\*BIOWGTR in the HRS tracker file). Since half the sample enters the extended interview including biomarker data in each biannual survey, I weight individuals by either their 2010 weight or their 2012 weight. This maximizes the available sample of both black and white respondents, and should approximately match the US population of the sample cohorts between 2010 and 2012. Statistical tests are adjusted for clustering and stratification using the R "survey" package [@lumleysurvey2023].

@@

tails_boot_fert <- map(cors_fert_edu, confint_workaround)

tails_boot_sibs <- map(cors_sibs_edu, confint_workaround)
